On Secure Delegation of SampBQP with a Classical Client

### 2020-02-08 qpip0.tex

\begin{lemma}[binding property of  Protocol~\ref{proto:urmila4}\cite{mahadev_delegation}]
If a prover's strategy result in passing the testing round with probability $1-\negl(n)$, then there must exist a $\rho$ such that $z$ is computationally indistinguishable with $\negl(n)$ error \hannote{add notation for comp indist.} from $M_{XZ}(\rho,h)$\hannote{add notation}, unless LWE can be efficiently solved by a quantum computer. 
\end{lemma}

@@

Denote $G_{i,\gamma}$ with  $\gamma$ found above as $G_i$.

@@

@@

First, We present a lemma from \cite{parallelrep}  that gives a decomposition of a cheating prover's state. We omit the proof here.

\begin{lemma}[Slight adaption from Lemma 3.5 of \cite{parallelrep}]\label{lem:partition}
Let $(U_0,U)$ be any prover's strategy in Protocol~\ref{proto:QPIP0samp}.  $i\in[m]$, 
$\gamma_0 \in[0,1]$, and $T\in \mathbb{N}$ such that $\frac{\gamma_0}{T}=1/\poly(\secpar)$. Let $\gamma$ be sampled uniformly randomly from $[\frac{\gamma_0}{T},\frac{2\gamma_0}{T},\dots,\frac{T\gamma_0}{T}]$. Then, there exists an efficient quantum procedure $G_{i,\gamma}$ such that for any (possibly sub-normalized) quantum state $\ket{\psi}_{\regX,\regZ}$,  
\begin{align*}
    G_{i,\gamma} \ket{0^m}_{\regC}\ket{\psi}_{\regX,\regZ}\ket{0^t}_{ph}\ket{0}_{th}\ket{0}_{in} = z_0\ket{0^m}_{\regC}\ket{\psi_{0}}_{\regX,\regZ}\ket{0^t01}_{ph,th,in}+ z_1\ket{0^m}_{\regC}\ket{\psi_{1}}_{\regX,\regZ}\ket{0^t11}_{ph,th,in} + \ket{\psi'_{err}}
\end{align*}
where $t$ is the number of qubits in the register $ph$, $z_0,z_1\in \mathbb{C}$ such that $|z_0|=|z_1|=1$, and 
$z_0$, $z_1$, $\ket{\psi_0}_{\regX,\regZ}$, $\ket{\psi_1}_{\regX,\regZ}$, and $\ket{\psi_{err}}_{\regX,\regZ}$ may depend on $\gamma$.

Furthermore, the following properties are satisfied.
%
\begin{enumerate}
%\item There exist (sub-normalized) states $\ket{\psi_0}_{\regX,\regZ}$ and $\ket{\psi_1}_{\regX,\regZ}$ such that when $G_{i,\gamma}$ runs on input $\ket{\psi}_{\regX,\regZ}$, the output is  $(0,\ket{\psi_0}_{\regX,\regZ}/\|\ket{\psi_0}_{\regX,\regZ}\|)$ with probability $\|\ket{\psi_0}_{\regX,\regZ}\|^2$, $(1,\ket{\psi_1}_{\regX,\regZ}/\|\ket{\psi_1}_{\regX,\regZ}\|)$ with probability $\|\ket{\psi_1}_{\regX,\regZ}\|^2$, and $\bot$ with probability  $1-\|\ket{\psi_0}_{\regX,\regZ}\|^2- \|\ket{\psi_1}_{\regX,\regZ}\|^2$,
    \item \label{partition-property-1} If we define $\ket{\psi_{err}}_{\regX,\regZ}\defeq \ket{\psi}_{\regX,\regZ} - \ket{\psi_{0}}_{\regX,\regZ}- \ket{\psi_{1}}_{\regX,\regZ}$, then we have  $E_{\gamma}[\|\ket{\psi_{err}}_{\regX,\regZ}\|^2]\leq \frac{6}{T}+\negl(n)$. 
\item For any fixed $\gamma$, $\Pr[M_{ph,th,in}\circ \ket{\psi'_{err}} \in \{0^t01,0^t11\}] =0$. %where $M_{ph,th,in}$ is the computational-basis measurement in the register $(ph,th,in)$. %and $t$ is the number of qubits in $ph$.   
This implies that if we apply the measurement $M_{ph,th,in}$ on $\frac{G_{i,\gamma} \ket{0^m}_{\regC}\ket{\psi}_{\regX,\regZ}\ket{0^t}_{ph}\ket{0}_{th}\ket{0}_{in}}{\|\ket{\psi}_{\regX,\regZ}\|}$, then the outcome is $0^tb1$ with probability $\|\ket{\psi_b}_{\regX,\regZ}\|^2$ and the resulting state in the register $(\regX,\regZ)$  is $\frac{\ket{\psi_b}_{\regX,\regZ}}{\|\ket{\psi_b}_{\regX,\regZ}\|}$ ignoring a global phase factor.
    \item For any fixed $\gamma$, $E_{b\in \{0,1\}} [\|\ket{\psi_b}_{\regX,\regZ}\|^2]\leq \frac{1}{2}\|\ket{\psi}_{\regX,\regZ}\|^2$. 
        \item 
For any fixed $\gamma$ and $c\in \bit^m$ such that $c_i=0$, we have 
\begin{align*}
\Pr\left[M_{\regX_i}\circ U\frac{\ket{c}_{\regC}\ket{\psi_0}_{\regX,\regZ}}{\|\ket{\psi_0}_{\regX,\regZ}\|}\in \Acc_{k_i,y_i}\right]\leq 2^{m-1}\gamma+\negl(\secpar).
\end{align*}
    \item 
For any fixed $\gamma$, there exists an efficient quantum algorithm $\ext_i$ such that 
\begin{align*}  
  \Pr\left[\ext_i\left(\frac{\ket{0^m}_{\regC}\ket{\psi_1}_{\regX,\regZ}}{\|\ket{\psi_1}_{\regX,\regZ}\|}\right)\in \Acc_{k_i,y_i}\right]=1-\negl(\secpar).
  \end{align*}   
\end{enumerate}
\end{lemma}

	where $t$ is the number of qubits in the register $ph$ \Ethan{Where is this register defined?},
	$z_0, z_1\in\bbC$ such that $\abs{z_0}=\abs{z_1}=1$, and $z_0$, $z_1$, $\ket{\psi_0}_{X, Z}$, $\ket{\psi_1}_{X, Z}$, $\ket{\psi_{err}}_{X, Z}$ may depend on $\gamma$.
	Furthermore, the following properties are satisfied.
	\begin{enumerate}
		\item Let $\ket{\psi_{err}}=\ket{\psi}-\ket{\psi_0}-\ket{\psi_1}$, then
			$$\E_\gamma[\norm{\ket{\psi_{err}}}^2]\leq\frac{1}{T}+\negl(n)$$
		\item TODO Some long property
		\item For any fixed $\gamma$,
			$$\E_{b\in\set{0, 1}}\left[\norm{\ket{\psi_{b}}_{X, Z}}^2\right]\leq\frac{1}{2}\norm{\ket{\psi}_{X, Z}}^2$$
		\item For any fixed $\gamma$ and $c\in\set{0, 1}^m$ such that $c_i=0$, \Ethan{Where's this $M_{X_i}$ defined?}
			$$\Pr\left[M_{X_i}\circ U\frac{\ket{c}_C\ket{\psi_0}_{X,Z}}{\norm{\psi_0}_{X,Z}}\in A_{k_i, y_i}\right]\leq2^{m-1}\gamma+\negl(n)$$
		\item For any fixed $\gamma$, there exists an efficient quantum algorithm $\cE_i$ such that
			$$\Pr\left[\cE_i\left(\frac{\ket{0^m}_C\ket{\psi_1}_{X,Z}}{\norm{\psi_1}_{X,Z}}\in A_{k_i, y_i}\right)\right]\leq1-\negl(n)$$
	\end{enumerate}
\end{lem}
\fi

\end{theorem}
\begin{proof}
We run Mahadev's 4-round protocol \ref{} and use parallel repetition to reduce the soundness error. \hannote{describe $N$ time para rep}. 
\end{proof}

\begin{lem}
	Let $m=O(\log n)$ \Ethan{$n$ is problem size?}, $\gamma_0\in[0, 1]$, and $T\in\bbN$ such that $\frac{\gamma_0}{T}=\frac{1}{\poly(n)}$.
	Let $\gamma_i\xleftarrow{\$}\set{\frac{j\gamma_0}{T}}^T_{j=1}$ \Ethan{This is a set, right? Doesn't look like one in the original document} for each $i\in[m]$.
	Then a state $\ket{psi}_{X, Z}$ can be partitioned as follows: \Ethan{Just gonna hard-code $c=0^m$ here for now}
	$$\ket{\psi}=\ket{\psi_0}+\ket{\psi_{10}}+\ket{\psi_{110}}+\ldots+\ket{\psi_{11\ldots10}}+\ket{\psi_{11\ldots11}}+\ket{\psi_{err}}$$
	where the way of partitioning may depend on the choices of $\hat\gamma=(\gamma_i)_{i=1}^m$.
	Furthermore, the following properties are satisfied. \Ethan{Takes a bit of parsing to see how is our case different here since $c$ might be defined differently for us}
	\begin{enumerate}
		\item stuff
		\item For any fixed $\hat\gamma$... 
		\item For any fixed $\hat\gamma$...
		\item For any fixed $c$,
			$$\E_{\hat\gamma}\left[\norm{\ket{\psi_{err}}_{X,Z}}^2\right]\leq\frac{6m^2}{T}+\negl(n)$$
		\item stuff
	\end{enumerate}
\end{lem}
    asdf
\begin{cor}

>>>>

\begin{lemma}[binding property of  Protocol~\ref{proto:urmila4}\cite{mahadev_delegation}]
If a prover's strategy\hannote{need clarification} result in passing the testing round with probability $1-\negl(n)$, then there must exist a $\rho$ such that $z$ is computationally indistinguishable with $\negl(n)$ error \hannote{add notation for comp indist.} from $M_{XZ}(\rho,h)$\hannote{add notation}, unless LWE can be efficiently solved by a quantum computer. 
\end{lemma}

@@

@@

First, We present a slight adaption of Lemma 3.5 of \cite{parallelrep}  that partitions the prover's internal state. We omit the proof here.

%$\frac{\gamma_0}{T}=1/\poly(\secpar)$
\begin{lemma}[partition lemma]\label{lem:partition}
Let $(U_0,U)$ be a prover's strategy in Protocol~\ref{proto:QPIP0samp}.  Let $i\in[m]$, 
$\gamma_0 \in[0,1]$, and $T\in \mathbb{N}$ such that $\gamma_0=1/\poly(n)$ and $T=\poly(n)$. Let $\gamma$ be a random number sampled uniformly from $\L[\frac{\gamma_0}{T},\frac{2\gamma_0}{T},\dots,\frac{T\gamma_0}{T}\R]$.

There exists an $\poly(n)$-sized quantum circuit $G_{i,\gamma}$ such that for all (possibly sub-normalized) \hannote{$n$-qubit?} quantum state $\ket{\psi}_{\regX,\regZ}$,  
\begin{align*}
    G_{i,\gamma} \ket{0^m}_{\regC}\ket{\psi}_{\regX,\regZ}\ket{0^t}_{ph}\ket{0}_{th}\ket{0}_{in} = \\ z_0\ket{0^m}_{\regC}\ket{\psi_{0}}_{\regX,\regZ}\ket{0^t01}_{ph,th,in}+  z_1\ket{0^m}_{\regC}\ket{\psi_{1}}_{\regX,\regZ}\ket{0^t11}_{ph,th,in} + \ket{\psi'_{err}}
\end{align*}
\hannote{what's wrong with all these registers} where $t$ is the number of qubits in the register $ph$, $z_0,z_1\in \mathbb{C}$ such that $|z_0|=|z_1|=1$, and 
$z_0$, $z_1$, \hannote{$Z$ just phase factor?}$\ket{\psi_0}_{\regX,\regZ}$, $\ket{\psi_1}_{\regX,\regZ}$, and $\ket{\psi_{err}}_{\regX,\regZ}$ may depend on $\gamma$.

Furthermore, the following properties are satisfied.
%
\begin{enumerate}
    \item \label{partition-property-1}  Define $\ket{\psi_{err}}_{\regX,\regZ}\defeq \ket{\psi}_{\regX,\regZ} - \ket{\psi_{0}}_{\regX,\regZ}- \ket{\psi_{1}}_{\regX,\regZ}$.\hannote{?} We have  $$E_{\gamma}[\|\ket{\psi_{err}}_{\regX,\regZ}\|^2]\leq \frac{6}{T}+\negl(n)$$. 
    $$E_{\gamma}[\|\ket{\psi}_{\regX,\regZ}\|^2 -\|\ket{\psi_0}_{\regX,\regZ}\|^2 -\|\ket{\psi_1}_{\regX,\regZ}\|^2]\leq \frac{6}{T}+\negl(n)$$
\item For any fixed $\gamma$, $\Pr[M_{ph,th,in}\circ \ket{\psi'_{err}} \in \{0^t01,0^t11\}] =0$. %where $M_{ph,th,in}$ is the computational-basis measurement in the register $(ph,th,in)$. %and $t$ is the number of qubits in $ph$.   
This implies that if we apply the measurement $M_{ph,th,in}$ on $\frac{G_{i,\gamma} \ket{0^m}_{\regC}\ket{\psi}_{\regX,\regZ}\ket{0^t}_{ph}\ket{0}_{th}\ket{0}_{in}}{\|\ket{\psi}_{\regX,\regZ}\|}$, then the outcome is $0^tb1$ with probability $\|\ket{\psi_b}_{\regX,\regZ}\|^2$ and the resulting state in the register $(\regX,\regZ)$  is $\frac{\ket{\psi_b}_{\regX,\regZ}}{\|\ket{\psi_b}_{\regX,\regZ}\|}$ ignoring a global phase factor.

    % \item For any fixed $\gamma$, $E_{b\in \{0,1\}} [\|\ket{\psi_b}_{\regX,\regZ}\|^2]\leq \frac{1}{2}\|\ket{\psi}_{\regX,\regZ}\|^2$. \hannote{redundant?}

        \item 
For any fixed $\gamma$ and $c\in [m]$ such that $c\neq i$\hannote{check}\hannote{for all k, y}, we have 
\begin{align*}
\Pr\left[M_{\regX_i}\circ U\frac{\ket{c}_{\regC}\ket{\psi_0}_{\regX,\regZ}}{\|\ket{\psi_0}_{\regX,\regZ}\|}\in \Acc_{k_i,y_i}\right]\leq (m-1)\gamma+\negl(\secpar).
\end{align*}
    \item 
For any fixed $\gamma$, there exists an efficient quantum algorithm $\ext_i$ such that 
\begin{align*}  
  \Pr\left[\ext_i\left(\frac{\ket{0^m}_{\regC}\ket{\psi_1}_{\regX,\regZ}}{\|\ket{\psi_1}_{\regX,\regZ}\|}\right)\in \Acc_{k_i,y_i}\right]=1-\negl(\secpar).
  \end{align*}   \hannote{$M_x?$}
\end{enumerate}
\end{lemma}

	where $t$ is the number of qubits in the register $ph$ \Ethan{Where is this register defined?},
	$z_0, z_1\in\bbC$ such that $\abs{z_0}=\abs{z_1}=1$, and $z_0$, $z_1$, $\ket{\psi_0}_{X, Z}$, $\ket{\psi_1}_{X, Z}$, $\ket{\psi_{err}}_{X, Z}$ may depend on $\gamma$.
	Furthermore, the following properties are satisfied.
	\begin{enumerate}
		\item Let $\ket{\psi_{err}}=\ket{\psi}-\ket{\psi_0}-\ket{\psi_1}$, then
			$$\E_\gamma[\norm{\ket{\psi_{err}}}^2]\leq\frac{1}{T}+\negl(n)$$
		\item TODO Some long property
		\item For any fixed $\gamma$,
			$$\E_{b\in\set{0, 1}}\left[\norm{\ket{\psi_{b}}_{X, Z}}^2\right]\leq\frac{1}{2}\norm{\ket{\psi}_{X, Z}}^2$$
		\item For any fixed $\gamma$ and $c\in\set{0, 1}^m$ such that $c_i=0$, \Ethan{Where's this $M_{X_i}$ defined?}
			$$\Pr\left[M_{X_i}\circ U\frac{\ket{c}_C\ket{\psi_0}_{X,Z}}{\norm{\psi_0}_{X,Z}}\in A_{k_i, y_i}\right]\leq2^{m-1}\gamma+\negl(n)$$
		\item For any fixed $\gamma$, there exists an efficient quantum algorithm $\cE_i$ such that
			$$\Pr\left[\cE_i\left(\frac{\ket{0^m}_C\ket{\psi_1}_{X,Z}}{\norm{\psi_1}_{X,Z}}\in A_{k_i, y_i}\right)\right]\leq1-\negl(n)$$
	\end{enumerate}
\end{lem}

\end{theorem}

\fi
==========

Denote $G_{i,\gamma}$ with  $\gamma$ found above as $G_i$. \hannote{finding $\gamma$ is not computationally efficient.}

====

@@

\begin{lem}
	Let $m=O(\log n)$ \Ethan{$n$ is problem size?}, $\gamma_0\in[0, 1]$, and $T\in\bbN$ such that $\frac{\gamma_0}{T}=\frac{1}{\poly(n)}$.
	Let $\gamma_i\xleftarrow{\$}\set{\frac{j\gamma_0}{T}}^T_{j=1}$ \Ethan{This is a set, right? Doesn't look like one in the original document} for each $i\in[m]$.
	Then a state $\ket{psi}_{X, Z}$ can be partitioned as follows: \Ethan{Just gonna hard-code $c=0^m$ here for now}
	$$\ket{\psi}=\ket{\psi_0}+\ket{\psi_{10}}+\ket{\psi_{110}}+\ldots+\ket{\psi_{11\ldots10}}+\ket{\psi_{11\ldots11}}+\ket{\psi_{err}}$$
	where the way of partitioning may depend on the choices of $\hat\gamma=(\gamma_i)_{i=1}^m$.
	Furthermore, the following properties are satisfied. \Ethan{Takes a bit of parsing to see how is our case different here since $c$ might be defined differently for us}
	\begin{enumerate}
		\item stuff
		\item For any fixed $\hat\gamma$... 
		\item For any fixed $\hat\gamma$...
		\item For any fixed $c$,
			$$\E_{\hat\gamma}\left[\norm{\ket{\psi_{err}}_{X,Z}}^2\right]\leq\frac{6m^2}{T}+\negl(n)$$
		\item stuff
	\end{enumerate}
\end{lem}
    asdf

\begin{cor}
